\cvsection{Work Experience}
\begin{cventries}
  \cventry
    {Full-Stack Developer} % Job title
    {Communere Ltd \link{https://communere.com/}{\faLink}} % Organization
    {London, England} % Location
    {Feb. 2020 - Present} % Date(s)
    {
        \textcolor{primary}{\textbf{SCHALA}}\break
        {It’s a web application (PWA) to help golf clubs and golfers manage their games with ease. Golf is a highly dynamic and complex game that we achieved to develop Schala to cover most of its complexity, developed Schala to support both real-time and offline mode at the same time. You can find the latest version of SCHALA from \link{http://schalagolf.com/}{Here}; Due to the size of the development team (2 developers) I need to work on different part of stack myself.}
        \begin{itemize}
            \item Design and Developed SCHALA from design to implementation.
            \item Developed multiple web scrapper using \textbf{Node.js} to extract the information's we need.
            \item \textbf{Front-end} 
            \cvtag{React}
            \cvtag{Redux} 
            \cvtag{Material-UI}
            \cvtag{TypeScript}
            \item \textbf{Back-end}  
            \cvtag{Node.js}
            \cvtag{Express}
            \cvtag{Socket.IO}
            \cvtag{Firebase}
            \cvtag{RethinkDB}
        \end{itemize}
        \textcolor{primary}{\textbf{Galen}}\break
        {It's A Website to help microbiologists create meaningful reports from bacteria sample data; I developed Galen front-end using \textbf{React} and \textbf{Pure CSS} using \textbf{styled-components} to develop a given design on \textbf{Figma}, developed a Rule-Engine and multiple endpoints of \textbf{GraphQL} API, Created a \textbf{UI-Kit} package to use across multiple projects with the same UI.}
        \begin{itemize}
        \item \textbf{Front-end} 
            \cvtag{React}
            \cvtag{GraphQL} 
            \cvtag{Apollo}
            \cvtag{TypeScript}
            \item \textbf{Back-end}  
            \cvtag{Node.js}
            \cvtag{GraphQL}
            \cvtag{Apollo}
            \cvtag{TypeScript}
            \cvtag{MySQL}
        \end{itemize}
        \textcolor{primary}{\textbf{COVID data catalogue}}\break
        {It's A simple website developed by \textbf{React} to gather various datasets such as images, databases, articles, and documents to help AI projects and scientist, We used \textbf{AppBase.io} as a data storage. You can find it From \link{https://coviddata.io/}{ Here}}\break
        \cvtag{React}
        \cvtag{AppBase.io}\break
    }
%---------------------------------------------------------
  \cventry
    {Full-Stack Developer} % Job title
    {Monotech \link{https://monotech.com.au/}{\faLink}} % Organization
    {Sydney, Australia} % Location
    {March. 2019 - Feb. 2020} % Date(s)
    {
        \textcolor{primary}{\textbf{Arian Travel}}\break
        {It's a travel agency ticket booking and E-Shop platform Developed using \textbf{React Native}, I developed this platform from scratch all on my own. You can find out the latest version on \link{https://apps.apple.com/us/app/arian-travel/id1484227707}{App Store}}
        \begin{itemize}
            \item \textbf{Front-end} 
            \cvtag{React Native}
            \cvtag{Redux} 
            \cvtag{NativeBase}
            \item \textbf{Back-end}  
            \cvtag{Node.js}
            \cvtag{Express}
            \cvtag{Mongoose}
        \end{itemize}
        \textcolor{primary}{\textbf{Persian Bakery}}\break
        {It's an online E-shop for bakeries and confectioneries in which users buy their products and see cooking time-table. I developed it from scratch using \textbf{React Native}. You can find out the latest version on \link{https://apps.apple.com/us/app/persian-bakery/id1483600529}{App Store} And \link{https://play.google.com/store/apps/details?id=au.com.persianbakeryco&hl=de_AT}{Google Play}}
        \begin{itemize}
            \item \textbf{Front-end} 
            \cvtag{React Native}
            \cvtag{Redux} 
            \cvtag{NativeBase}
            \item \textbf{Back-end}  
            \cvtag{Node.js}
            \cvtag{Express}
            \cvtag{Mongoose}
        \end{itemize}
    }
%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {ATRAS} % Organization
    {} % Location
    {June 2017 - Jan 2019} % Date(s)
    {
        \textcolor{primary}{\textbf{Electrical Tower Inspector}}\break
        {It's an android application which controls DJI Drones to autonomously fly over electrical tower and captures images.}    
        \begin{itemize}
            \item Implemented a Native java application to connect DJI Drones
            \item Improvise new ideas to solve various problems
            \item Reduced GPS Error from 1.5-2 meter to less than 0.5 meter
        \end{itemize}
        \textcolor{primary}{\textbf{DJI Live Broadcaster over WebRTC}}\break
        {It's an android application which captures DJI Drones video and broadcast it on a WebRTC Channel.}\break
        \cvtag{Android Native}
        \cvtag{DJI SDK}
        \cvtag{Intel WebRTC SDK}
        \break
    }   
%---------------------------------------------------------
  \cventry
    {} % Job title
    {Personal Projects} % Organization
    {} % Location
    {} % Date(s)
    {
        \textcolor{primary}{\textbf{Waterbase}}\break
        {It's a general CRUD server developed using Node.js for fast production inspired that supports both WebSocket and restful API by Firebase real-time database. developers can easily set the tables list in the config file and use crud endpoints.}\break
        \cvtag{Node.js}
        \cvtag{Websocket}
        \cvtag{REST}\break
        \textcolor{primary}{\textbf{Data Synchroniser}}\break
        {It's a \textbf{Node.js}, \textbf{TypeScript} Server Application which synchronizes data between an Accounting Application and a CRM.}\break
        \cvtag{Node.js}
        \cvtag{TypeScript}\break
        \textcolor{primary}{\textbf{Smart Wallpaper}}\break
        {It's an android native application that automatically changes phone wallpaper inspired by the Wallpapers app developed by Google.}\break
        \cvtag{Android Native}
    }
%---------------------------------------------------------
\end{cventries}
