%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Fullstack-Developer} % Job title
{Communer Ltd} % Organization
{Full-time , Remote, London} % Location
{Jun. 2020 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\textcolor{awesome-red}{{\textbf{Membermatch}}}
\break
{\it Developed a project that helps golfers plan matches,play game and meet other golfers - React/Node.js Developer}
\break
{\textbf{ Stack:} }{Node.js, Express, React, Typescript, Redux, Material UI, RethinkDB, Socket.io, Firebase}
\break
\begin{cvitems}
\item {Refactored \& developed the React web application }
\item {Developed Node.js API}
\item {Used socket.io for realtime scoring}
\item {Implemented a sub-system for calculating Handicaps \& Individual/Team scores based on different game rules}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Full-Stack Developer} % Job title
{Radshid} % Organization
{Full-time} % Location
{Mar. 2012 - Dec. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\textcolor{awesome-red}{{\textbf{Power Plant PDA}}}
\break
{\it Designing a Power Plant data collector system - Lead Developer}
\break
{\textbf{ Stack:} }{.Net Core API, React, React Native, Redux, Material UI, SQL Server, EF, SQLite}
\break
\begin{cvitems}
\item {Removed paper sheets from the whole data logging process.}
\item {Defined the whole Power Plant by designing dynamic forms and RFID Tags}
\item {Designed a great UI/UX in the operator's app(react native app on PDAs) to work in an industrial environment.}
\item {Designed a creative and user-friendly UI for admin panel with react.js that totally made clients satisfied}
\end{cvitems}
\bigskip
\break
\bigskip
\textcolor{awesome-red}{{\textbf{Fleet Management System}}}
\break
{\it Analyzed and Designed a fleet-management system from scratch. Lead Developer - DB Admin}
\break
{\textbf{ Stack:} }{WCF Service, C\# Windows Services, ASP.Net, SQL Server, EF, JQuery, Map API, Javascript, Bootstrap}
\break
\begin{cvitems}
\item {70\% improved performance of live view and tracking page.}
\item {Increased active clients up to 20\% by adding an automatic reporting system.}
\item {Improved customer service team performance by adding an auto diagnostic system.}
\item {Implemented multi-thread Avl Manager service to deserialize more than 2 million locations per day.}
\item {Attracted more organizational customers by designing a report builder system.}
\item {Teamwork with electronic engineers for designing AVL's negotiation protocol on TCP}
\end{cvitems}
}


%------------------------------------------------

\cventry
{.Net Developer} % Job title
{Freelancer} % Organization
{} % Location
{Oct. 2010 - Mar. 2012} % Date(s)
{ % Description(s) of tasks/responsibilities
{\textbf{ Stack:} }{ASP.Net, C\# Windows Services, SQL Server, EF, JQuery, Bootstrap}
\break
\begin{cvitems}
\item {Implemented a simple BMS system for hotels/dorms.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{.Net Developer} % Job title
{Arico} % Organization
{Part-time} % Location
{Dec. 2008 - Oct. 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
{\textbf{ Stack:} }{ASP.Net, C\#, SQL Server, ADO.Net}
\break
\begin{cvitems}
\item {ASP.Net \& C\# Developer}
\item {Developed payment and financial software}
\item {Developed a project manager service based on the PMBOK standard}
\end{cvitems}
}

\end{cventries}